Thermodynamic fragments in magic state theories

### 2020-12-04 magic_paper.tex
Corrected typos

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} < x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$, we can always interpolate between the origin and the first target state elbow, so that
\begin{equation}
	L'_\star = \frac{x_\star}{x'_0}L_0 = \frac{1}{9^{\nn-\tt}}\Phi_+\left(0;\tt,\frac{12-4\epsilon}{15-8\epsilon}\right) = \frac{(3-4\epsilon)^{\tt}}{9^{\nn}}.
\end{equation}
The process in~\cref{eq:sudist} is therefore possible if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{\nn}{\tt} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
\end{align}
As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
\nick{All numerical examples I have tested, for various different cases, are quite close}

>>>>

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can always interpolate between the origin and the first target state elbow, 
\begin{equation}
	\begin{split}
	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{\nn-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
	&= \frac{(3-4\epsilon')^{\tt}}{9^{\nn}}.
	\end{split}
\end{equation}
The process in~\cref{eq:sudist} is therefore possible if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{\nn}{\tt} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
\end{align}
As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
\nick{All numerical examples I have tested, for various different cases, are quite close}
